He-Man: A domain-specific language for lightweight concurrency

### 2011-12-10 report/report.tex
Start report.
Started on report.

\documentclass{article}
\usepackage{cite}
\renewcommand{\t}{\texttt}

\title{15-744 Project Proposal}
\author{Carlo Angiuli \and Michael Sullivan}
\date{September 28, 2011}

@@

% Needs to include:
%  - problem statement
%  - state-of-the-art
%  - work plan / milestones

\section{Motivation}

Modern network applications need to support many simultaneous clients---this is
known as the C10K (``10,000 client'') problem\cite{Kegel}. But to maintain these
simultaneous connections, an application must track each client's state
independently. A straightforward way to do this is to spawn a thread for each
client, but this approach does not scale as the number of clients grows.

@@

\section{Proposal}

@@

The back-end of this system can be implemented via several different options
which we are still evaluating. One option is to directly interface with the
\t{epoll} hooks in the Haskell runtime system, bypassing the native lightweight
threads. Another option is to generate C source code which itself implements the
network application, optionally linkable with native C code.

\section{Milestones}

We will first collect a representative sample of Linux network applications and
examine the range of high-level primitives required to support them. We will
then decide on a specific back-end for our language, and design the front- and
back-end in tandem. To evaluate the utility of this language, we will build a
number of representative applications in our language (e.g., an echo server,
simple HTTP server) and compare them to traditional implementations, with
respect to both code simplicity and performance.

>>>>

\documentclass{article}
\usepackage{cite}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black,citecolor=black]%
{hyperref}
\renewcommand{\t}{\texttt}

\title{He-Man: A domain-specific language for lightweight concurrency}
%\subtitle{I said hey, what's goin' on}
\author{Carlo Angiuli \and Michael Sullivan}
\date{December 12, 2011}

@@

\section{Introduction}

Modern network applications need to support many simultaneous clients---this is
known as the C10K (``10,000 client'') problem\cite{Kegel}. Modern servers have
enough memory and network resources to support this many

To maintain these simultaneous connections, an application must maintain each
client's state independently;

while 
block each one

The simplest way to do this is to spawn a thread for each client, but this
approach does not scale as the number of clients grows.

@@

Because

@@

Generate C source code which itself implements the network application, linkable
with native C code.

simple runtime

\section{Related work}

The Nginx\cite{Nginx} and Lighttpd\cite{Lighttpd} HTTP servers use an
event-based architectures, unlike Apache's threads\cite{Apache}, with the
specific goal of addressing the C10k problem,

Haskell event loop stuff: \cite{LiZdancewic}

Haskell has epoll support and lightweight threads

Erlang

\section{Front-end}

\section{Back-end}

\section{Performance}

Each thread takes up XXX memory (see Memory.hs)

HTTP server performance is XXX

\section{Future work}

\section{Conclusions}
